Analytic Doppler Imaging

### 2019-07-30 tex/gitlinks.tex
terrible notation

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/54ab337d6e461cf208c768298131f9cd7e577ad7/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/028c5691ad07f44dc9bd359433907a5c2863b82c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
